{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-02-29 Paper_ttbarH_Draft.tex
Changes on secII based on Ken's corrections

and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs
{\bf KK: ``boson''? I don't think PRD allows us to just say ``Higgs''}. \par

@@

%%%%%%%%%%%%%%%%% FIGURA 2 %%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{figure}[th]
\centering
\includegraphics[scale=0.6]{esquematico_II.pdf}
\vspace*{0.02\textwidth}
\caption{Schematic representation of the process $g_ag_b\to t(\to
  b_i{\ell}^+\nu_{\ell})\tbar(\to \bbar_j {\ell}^- \nubar) H$. The
  indices $i,j$ denote the colour of the quarks while $a,b$ are gluon
  indices.}
\label{fig2}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To derive the above expressions, we begin by considering the
schematic representation for the process $g_ag_b\to t(\to
b_i{\ell}^+\nu_{\ell})\,\tbar(\to \bbar_j {\ell}^- \nubar)\,H$
that is sketched in Fig.~\ref{fig2}.
Here $a$ and $b$ denote the initial-state gluons and
$i$ and $j$ refer to the colours of the top and antitop quarks.
%\par
%
The amplitude for this process may be written in the following
compact form
%
\beq
\label{eq6}
\mathcal{M}^{ab,ij}=\bar{\psi}_t\,\mathcal{A}^{ab,ij}\,\psi_{\tbar}\,,
\eeq
%
where the spinors $\bar{\psi}_t$ and $\psi_{\tbar}$
contain all of the information regarding the decay of the
virtual top and anti-top, respectively,
and where the quantity $A^{ab,ij}$ is given by
%
\beq
\label{eq5}
\mathcal{A}^{ab,ij}\equiv A^{ab,ij}_{\mu\nu}(\epsilon_{\lambda_a})^{\mu}(\epsilon_{\lambda_b})^{\nu}=\sum_{k=1}^8 \mathcal{A}^{ab,ij}_k =\kp \sum_{k=1}^8 \mathcal{S}^{ab,ij}_k + i\kpt \sum_{k=1}^8 \mathcal{P}^{ab,ij}_k.
\eeq 
%
The sum over $k$ in the above expression
corresponds to the eight gluon-initiated
diagrams indicated in Fig.~\ref{fig1} {\bf (KK: correct?)}; also,
$\epsilon_{\lambda_a}$ and $\epsilon_{\lambda_b}$ are the
polarization vectors corresponding to $g_a$ and $g_b$, respectively.
In the last equality in Eq.~(\ref{eq5})
we have explicitly separated the amplitude into
two sums, with one sum corresponding to the scalar contributions
and the other to the pseudoscalar ones.
Taking all of the final-state particles to be massless, we can use the
spinor techniques
developed in \cite{Kleiss} to write $\bar{\psi}_t$ and
$\psi_{\tbar}$ as follows\footnote{These spinor techniques can also be used
  for massive final-state particles. Given the
  energy scale involved in the process in question, however, the assumption
  of massless final-state particles is sensible and greatly
  simplifies the derivation of Eq.~(\ref{eq2}).}
%
\bea
\label{eq7}
\bar{\psi}_t &=& -g^2\, \mathbb{P}_t(t)\,\mathbb{P}_W(t-b)\,
   \langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\
\label{eq8}
\psi_{\tbar} &=& -g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
   \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
\eea
%
where $|i+(-)\rangle \equiv (1/2)(1\pm \gamma^5)\,\psi_i$
represents a right-handed (left-handed) chiral spinor for final-state
particle $i$ and $\langle i+(-)|$ represents the corresponding adjoint spinor.
{\bf (KK: Do we mean the adjoint spinor, related by $C \psi^T$,
  or whatever?)}
Also, $\mathbb{P}_t(q)=(q^2-m^2_t+im_t\Gamma_t)^{-1}$ and
$\mathbb{P}_W(q)=(q^2-M^2_W+im_W\Gamma_W)^{-1}$, and
we have denoted the momenta of the various particles by the symbols
that refer to the names of those particles~\cite{Mangano}.

>>>>

and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs boson. \par

@@

%%%%%%%%%%%%%%%%% FIGURA 2 %%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{esquematico_II.pdf}
\vspace*{0.02\textwidth}
\caption{Schematic representation of the process $g_ag_b\to t(\to
  b_i{\ell}^+\nu_{\ell})\tbar(\to \bbar_j {\ell}^- \nubar) H$. The
  indices $i,j$ denote the colour of the quarks while $a,b$ are gluon
  indices.}
\label{fig2}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To derive the above expressions, we begin by considering the
schematic representation for the process $g_ag_b\to t(\to
b_i{\ell}^+\nu_{\ell})\,\tbar(\to \bbar_j {\ell}^- \nubar)\,H$
that is sketched in Fig.~\ref{fig2}.
Here $a$ and $b$ denote the initial-state gluons and
$i$ and $j$ refer to the colours of the top and antitop quarks.
%\par
%
The amplitude for this process may be written in the following
compact form
%
\beq
\label{eq6}
\mathcal{M}^{ab,ij}=\bar{\psi}_t\,\mathcal{A}^{ab,ij}\,\psi_{\tbar}\,,
\eeq
%
where the spinors $\bar{\psi}_t$ and $\psi_{\tbar}$
contain all of the information regarding the decay of the
virtual top and anti-top, respectively,
and where the quantity $A^{ab,ij}$ is given by
%
\beq
\label{eq5}
\mathcal{A}^{ab,ij}\equiv A^{ab,ij}_{\mu\nu}(\epsilon_{\lambda_a})^{\mu}(\epsilon_{\lambda_b})^{\nu}=\sum_{k=1}^8 \mathcal{A}^{ab,ij}_k =\kp \sum_{k=1}^8 \mathcal{S}^{ab,ij}_k + i\kpt \sum_{k=1}^8 \mathcal{P}^{ab,ij}_k.
\eeq 
%
The sum over $k$ in the above expression
corresponds to the eight gluon-initiated
diagrams indicated in Fig.~\ref{fig1}; also,
$\epsilon_{\lambda_a}$ and $\epsilon_{\lambda_b}$ are the
polarization vectors corresponding to $g_a$ and $g_b$, respectively.
In the last equality in Eq.~(\ref{eq5})
we have explicitly separated the amplitude into
two sums, with one sum corresponding to the scalar contributions
and the other to the pseudoscalar ones.
Taking all of the final-state particles to be massless, we can use the
spinor techniques
developed in \cite{Kleiss} to write $\bar{\psi}_t$ and
$\psi_{\tbar}$ as follows\footnote{These spinor techniques can also be used
  for massive final-state particles. Given the
  energy scale involved in the process in question, however, the assumption
  of massless final-state particles is sensible and greatly
  simplifies the derivation of Eq.~(\ref{eq2}).}
%
\bea
\label{eq7}
\bar{\psi}_t &=& -g^2\, \mathbb{P}_t(t)\,\mathbb{P}_W(t-b)\,
   \langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\
\label{eq8}
\psi_{\tbar} &=& g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
   \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
\eea
%
where $|i+(-)\rangle \equiv (1/2)(1\pm \gamma^5)\,\psi_i$
represents a right-handed (left-handed) chiral spinor for final-state
particle $i$ and $\langle i+(-)|$ represents the corresponding adjoint spinor.
{\bf (KK: Do we mean the adjoint spinor, related by $C \psi^T$,
  or whatever?)}
Also, $\mathbb{P}_t(q)=(q^2-m^2_t+im_t\Gamma_t)^{-1}$ and
$\mathbb{P}_W(q)=(q^2-m^2_W+im_W\Gamma_W)^{-1}$, and
we have denoted the momenta of the various particles by the symbols
that refer to the names of those particles~\cite{Mangano}.
